Indexes measures for oak decline severity using phenotypic descriptors

### 2019-07-03 outline/outline.Rmd
adjustment to outline

**Figure 1:** 
    - a) Site differences MDS plot
    - b) Site difference feature importance
    - c) Example of site correction effect on a descriptor

**Figure 2:** Decline index scales (graphical representations of the indexes)

**Figure 3:** Decline index descriptor contributions

**Figure 4:** Top ranked descriptor response surfaces

**Figure 5:** Decline indexes versus manual status assignments

>>>>

**Figure 1:** 
    - a) Site differences MDS plot
    - b) Site difference feature importance

**Figure 2:** Example of site correction effect on a descriptor

**Figure 3:** Decline index scales (graphical representations of the indexes)

**Figure 4:** Decline index descriptor contributions

**Figure 5:** Top ranked descriptor response surfaces

**Figure 6:** Decline indexes versus manual status assignments
